The resevol package

### 2022-06-28 notebook/index.Rmd
Finish up a notebook entry explaining the new custom om landscape feature

```{r, echo = FALSE}
printf(custom_terrain);
```

@@

```{r}
sim       <- run_farm_sim(mine_output = mg_n1, N = 100, 
                          repro = "asexual", time_steps = 10,
                          terrain = complex_terrain,
                          print_inds = FALSE, print_gens = FALSE,
                          print_last = FALSE, get_stats = FALSE);
```

>>>>

```{r, echo = FALSE}
print(custom_terrain);
```

@@

```{r}
sim       <- run_farm_sim(mine_output = mg_n1, N = 100, 
                          repro = "asexual", time_steps = 10,
                          crop_number = 4, pesticide_number = 3,
                          terrain                 = complex_terrain,
                          food_consume            = c(0.25, 0.25, 0.25, 0),
                          pesticide_consume       = c(0.1, 0.1, 0),
                          crop_init               = initial_crops,
                          crop_rotation_type      = crop_cycle,
                          pesticide_init          = initial_pesticides,
                          pesticide_rotation_type = pesticide_cycle,
                          print_inds = FALSE, print_gens = FALSE,
                          print_last = FALSE, get_stats = FALSE);
```

The output shows that the pests leave the 'food' on the river alone (see layer 5), while the reserve (see layer 4) gets used very much.

```{r, echo = FALSE}
print(sim[[2]][,,1:5]);
```

Similarly, the pests will only be affected by pesticides 1 and 2, while 3 is effectively nothing. Note that this is of course a trick for modelling landscape areas without food or pesticide, but I do not see a reason to make this more explicit in the function (unless I receive requests due to confusion, but my hope is it is clear from these notes and documentation).
